---
title: "GVPT728 Project Final Code"
author: "Yael Beshaw"
date: "2025-01-23"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Download Potentially Necessary Packages
```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidycensus)
library(dplyr)
library(readr)
library(readxl)
library(haven)
library(ggfortify)
library(car)
library(huxtable)
library(lmtest)
library(ggdist)
library(fixest)
library(sandwich)
library(lmtest)
library(lme4)
library(modelsummary)
library(tableone)
library(knitr)
library(gt)
library(marginaleffects)
library(ggeffects)
library(labelled)
library(kableExtra)
```

# Import Original Dataset
```{r}
hints6 <- read_sav("/Users/yaelbeshaw/R Scripts and Projects/NYU-APSTA-GE-2011/HINTS6_SPSS/hints6_public.sav")
```

# Variables of Interest for this Study

## Dependent Variable

*Health Information-Seeking Behaviors:*

Electronic2_HealthInfo: "In the past 12 months, have you used the Internet to 
look for health or medical information?" (Binary)

## Independent Variable

*Frequency of Internet Usage:*

SocMed_Visited: Frequency of visiting social media sites in the past
12 months (ordinal or categorical).


## Controls

*Internet Access*

Type of internet access

1. Internet_DialUp
2. Internet_HighSpeed
3. Internet_Cell


*Device ownership or access*

HAVEDEVICE_CAT

*Access Satisfaction*

InternetConnection: Satisfaction with internet connection for health-related 
needs (ordinal scale).


*Health Literacy:*

ConfidentInternetHealth: "How confident are you that you can find helpful 
health resources on the Internet?" (Ordinal scale)


*Trust in Information:*

MisleadingHealthInfo: "How much of the health information that you see on social
media do you think is false or misleading?" (Ordinal scale)


*Health Status:*

EverHadCancer

MedConditions_Diabetes, MedConditions_HighBP, MedConditions_HeartCondition, 
MedConditions_LungDisease, MedConditions_Depression


*Demographics:*

Age; Age and AgeGrpB

Gender; BirthGender

Race; RaceEthn5

Educational attainment; EducA

Geographic: CENSDIV

Urban vs Rural; PR_RUCA_2010: USDA 2010 Primary Rural-Urban Community Area Code


*Economic Factors:* 

Income; HHInc

Employment: WorkFullTime(R4)

How many children: ChildrenInHH

*Stratum Classification*

STRATUM

HR High minority rural area 
HU High minority urban area
LR Low minority rural area
LU Low minority urban area

*Household ID*

HHID


# Select Variables

```{r}
select_data <- hints6 |>
  select(Electronic2_HealthInfo, #binary 1 or 2 *done
         UseInternet, #binary 1 or 2 *done
         SocMed_Visited, # 1 to 5 (every day to never) --flip *done
         Internet_DialUp, # binary 1 or 2 *done
         Internet_HighSpeed, # binary 1 or 2 *done
         Internet_Cell, # binary 1 or 2 *done
         HAVEDEVICE_CAT, #recode 4 as 0 *done
         InternetConnection, # 1 to 5 (extremely satisfied to not at all) -flip *done
         ConfidentInternetHealth, #1 to 5 (completely confident to not at all) -flip *done
         MisleadingHealthInfo, #1 to 5 (a lot to none (4), I dont use social (5)) -flip with 1 =0 *done
         EverHadCancer, #dummy- healthstatus *done
         MedConditions_Diabetes, #dummy - healthstatus *done
         MedConditions_HighBP, #dummy- healthstatus *done
         MedConditions_HeartCondition, #dummy - healthstatus *done
         MedConditions_LungDisease, #dummy- healthstatus *done
         MedConditions_Depression, #dummy- healthstatus *done
         Age, #continuous (18 to 99) use AgeGrpB for visualization *done
         BirthGender, # 0 == Male, 1 == Female *done
         RaceEthn5, # NHWhite, NHBlack, Hispanic, NHAsian, NHOther *done
         EducA, # Less than HS, HS, Some College, Collge and Beyond *done
         CENSDIV, # New England, Middle Atlantic, E/W North Central, South Atlantic, E/W South Central, Mountain, Pacific *done
         PR_RUCA_2010, # Metropolitan, Micropolitian, Small Town, Rural (code 0 or 1) *done
         HHInc, # 1 to 5, increasing *done
         WorkFullTime, # 1 or 2 0,1 *done
         ChildrenInHH, # 0 to 9 *done
         AgeGrpB,
         HHID)
```

# Data Preprocessing

Remove any missing data
```{r}
clean_data <- select_data %>%
  mutate(across(everything(), ~ na_if(., -9))) %>%
  mutate(across(everything(), ~ na_if(., -7))) %>%
  mutate(across(everything(), ~ na_if(., -6))) %>%
  mutate(across(everything(), ~ na_if(., -5))) %>%
  mutate(across(everything(), ~ na_if(., -4))) %>%
  mutate(across(everything(), ~ na_if(., -2)))


data <- na.omit(clean_data)
```

# Join the new dataset with the stratum assignment using HHID, use later

```{r}
stratum <- hints6 |>
  select(HHID,
         STRATUM)

data <- inner_join(data, stratum, by = "HHID")
```


# Recodes

```{r}

#For Binary Variables- Code 1's and 2's to 0 and 1

#DV
data$Electronic2_HealthInfo <- ifelse(data$Electronic2_HealthInfo == 1,
                                      1, 0)
# Type of Internet
data$Internet_DialUp <- ifelse(data$Internet_DialUp == 1,
                                      1, 0)
data$Internet_HighSpeed <- ifelse(data$Internet_HighSpeed == 1,
                                      1, 0)
data$Internet_Cell <- ifelse(data$Internet_Cell == 1,
                                      1, 0)

#Gender
data$BirthGender <- ifelse(data$BirthGender == 1,
                                      1, 0)

#Employment
data$WorkFullTime<- ifelse(data$WorkFullTime == 1,
                                      1, 0)


# Flip the ordinal variables from least to greatest

#Fr(SM)
data$SocMed_Visited <- factor(data$SocMed_Visited, 
                                 levels = c(5, 4, 3, 2, 1))
levels(data$SocMed_Visited) <- c("1", "2", "3", "4", "5")


# Internet Connection Satisfaction
data$InternetConnection <- factor(data$InternetConnection, 
                                 levels = c(5, 4, 3, 2, 1))
levels(data$InternetConnection) <- c("1", "2", "3", "4", "5")


# Confidence in Getting Health Info (Literacy)
data$ConfidentInternetHealth <- factor(data$ConfidentInternetHealth, 
                                 levels = c(5, 4, 3, 2, 1))
levels(data$ConfidentInternetHealth) <- c("1", "2", "3", "4", "5")


# Trust in Health Info on SM
data$MisleadingHealthInfo <- factor(data$MisleadingHealthInfo, 
                                 levels = c(5, 4, 3, 2, 1))
levels(data$MisleadingHealthInfo) <- c("1", "2", "3", "4", "5")


#Recode Variables

# Rural vs Not
data$PR_RUCA_2010 <- ifelse(data$PR_RUCA_2010== 1 |
                              data$PR_RUCA_2010== 4|
                              data$PR_RUCA_2010== 7,
                            0,
                            1)

# Any chronic conditions + cancer as a 1 or 0
data$HealthStatus <- ifelse(data$EverHadCancer == 1 | 
                                data$MedConditions_Diabetes == 1 | 
                                data$MedConditions_HighBP == 1 | 
                                data$MedConditions_HeartCondition == 1 | 
                                data$MedConditions_LungDisease == 1 | 
                                data$MedConditions_Depression == 1, 
                                1, 
                                0)

# Devices, none is 0 and multiple is 4 instead
data$HAVEDEVICE_CAT <- ifelse(data$HAVEDEVICE_CAT == 4, 0, 
                                  ifelse(data$HAVEDEVICE_CAT == 5, 4, 
                                         data$HAVEDEVICE_CAT))


# Turn internet type into one variable
data$InternetAccessType <- NA

# Assign any combinations as 4 = Multiple
data$InternetAccessType[data$Internet_DialUp == 1 & 
                         data$Internet_HighSpeed == 1] <- 4

data$InternetAccessType[data$Internet_DialUp == 1 & 
                         data$Internet_Cell == 1] <- 4

data$InternetAccessType[data$Internet_HighSpeed == 1 & 
                         data$Internet_Cell == 1] <- 4

# Assign individual categories as their own
data$InternetAccessType[data$Internet_DialUp == 1 & 
                         is.na(data$InternetAccessType)] <- 1

data$InternetAccessType[data$Internet_HighSpeed == 1 & 
                         is.na(data$InternetAccessType)] <- 2

data$InternetAccessType[data$Internet_Cell == 1 & 
                         is.na(data$InternetAccessType)] <- 3


# Recode the number of children, 0 = None up to 3+

data$ChildrenInHH_recode <- ifelse(data$ChildrenInHH >= 3, 3, as.character(data$ChildrenInHH))
```

# Descriptive Statisitics Visualizations

## Dependent VAR

```{r}
#DEPENDENT VARIABLE

freq_table <- table(data$Electronic2_HealthInfo)

pie(freq_table, 
    main = "In the Past 12 months, \n have you used the Internet to look for \n health or medical information?", 
    col = c("lightblue", "lightgreen"),
    labels = paste(names(freq_table), "\n", freq_table))
```
Compare the results against how many people use the internet in general
```{r}
freq_table <- table(data$ UseInternet)

pie(freq_table, 
    main = "Do you ever go on-line to access the Internet \n or World Wide Web,\n or to send and receive e-mail?", 
    col = c("lightblue", "lightgreen"), 
    labels = paste(names(freq_table), "\n", freq_table)) 
```

## Independent VAR

```{r}
freq_table <- table(data$SocMed_Visited)

x_labels <- c("Never \n n=822", "Rarely \n n=279", "Occasionally \n n=366", "Frequently \n n= 589", "Every Day \n n=2735") 

# Create the barplot
barplot(freq_table, 
        main = "In the last 12 months, \n how often did you visit a \n social media site?", 
        xlab = "Social Media Usage Frequency", 
        ylab = "Count", 
        col = "lightblue", 
        border = "white", 
        las = 1,  
        ylim = c(0, max(freq_table) + 5),
        names.arg = x_labels) 
```

## Health Information Related Controls

```{r}

#internet type
freq_table <- table(data$InternetAccessType)

names(freq_table) <- c("Dial-Up", "High-Speed", "Cellular", "Multiple")

category_count_table <- data.frame(
  Category = names(freq_table),
  Count = as.vector(freq_table)
)

kable(category_count_table, 
      caption = "Access Type")


#device type
freq_table <- table(data$HAVEDEVICE_CAT)

names(freq_table) <- c("Tablet Computer Only", "Smartphone Only", "Basic Cell Only",
                       "None", "Multiple Devices")

category_count_table <- data.frame(
  Category = names(freq_table),
  Count = as.vector(freq_table)
)

kable(category_count_table, 
      caption = "Device Type")


#health literacy

freq_table <- table(data$ConfidentInternetHealth)

x_labels <- c("Not at All \n n=206", "A Little \n n=413", "Somewhat \n n=1888", "Very \n n=1692", "Completely \n n=592") 

# Create the barplot
barplot(freq_table, 
        main = "How confident are you that you can find helpful \n health resources on the Internet?", 
        xlab = "Confidence", 
        ylab = "Count", 
        col = "lightgreen", 
        border = "white", 
        las = 1, 
        ylim = c(0, max(freq_table) + 5),  
        names.arg = x_labels)  

#trust in health information on social media

freq_table <- table(data$MisleadingHealthInfo)

x_labels <- c("No Social Media \n n=787", "None \n n=54", "A Little \n n=689", "Some \n n=1818", "A Lot \n n=1443") 

barplot(freq_table, 
        main = "How much of the health information that you see on social media \n do you think is false or misleading?", 
        xlab = "Trust in Health Information", 
        ylab = "Count", 
        col = "lightblue", 
        border = "white", 
        las = 1,  
        ylim = c(0, max(freq_table) + 5), 
        names.arg = x_labels) 
```

# Demographic Controls

```{r}
#DEMOGRAPHIC CONTROLS

# Health Status
freq_table <- table(data$HealthStatus)

pie(freq_table, 
    main = "Have you ever had Cancer or another Chronic Condition? \n (i.e., Diabetes, High BP, Heart Condition, Lung Disease, Depression)", 
    col = c("lightblue", "lightgreen"),
    labels = paste(names(freq_table), "\n", freq_table))

# Age
median(data$Age)

freq_table <- table(data$AgeGrpB)

x_labels <- c("18-34 \n n=782", "35-49 \n n=1048", "50-64 \n n=1408", "65-74 \n n=1015", "75+ \n n=538") 

barplot(freq_table, 
        main = "Age Groups of Respondents", 
        xlab = "Age", 
        ylab = "Count", 
        col = "lightblue", 
        border = "white", 
        las = 1,  
        ylim = c(0, max(freq_table) + 5),  
        names.arg = x_labels) 

# SEX at BIRTH
freq_table <- table(data$BirthGender)

pie(freq_table, 
    main = "Sex/Gender Assigned at Birth", 
    col = c("lightblue", "lightpink"),
    labels = paste(names(freq_table), "\n", freq_table),
    radius = 1, 
    cex = 1.2,  
    clockwise = TRUE,  
    border = "black",  
    init.angle = 90  
)

# Race
freq_table <- table(data$RaceEthn5)

names(freq_table) <- c("NHWHite", "NHBlack", "Hispanic",
                       "NHAsian", "NHOthers")

category_count_table <- data.frame(
  Category = names(freq_table),
  Count = as.vector(freq_table)
)

kable(category_count_table, 
      caption = "Race")


# Education
freq_table <- table(data$EducA)

names(freq_table) <- c("< High School", "High School Grad", "Some College",
                       "College Grad +")

category_count_table <- data.frame(
  Category = names(freq_table),
  Count = as.vector(freq_table)
)

kable(category_count_table, 
      caption = "Education")


# Rural vs Not
freq_table <- table(data$PR_RUCA_2010)

pie(freq_table, 
    main = "Rural vs Not", 
    col = c("lightblue", "lightgreen"),
    labels = paste(names(freq_table), "\n", freq_table),
    radius = 1,  
    cex = 1.2,  
    clockwise = TRUE,  
    border = "black",  
    init.angle = 180  
)

# How many Children Under 18

freq_table <- table(data$ChildrenInHH_recode)

x_labels <- c("0 Children \n n=3602", "1 Child \n n=576", "2 Children \n n=383", "3+ Children \n n=230") 

# Create the barplot
barplot(freq_table, 
        main = "# of Children Under 18", 
        xlab = "Ranges", 
        ylab = "Count", 
        col = "lightblue", 
        border = "white", 
        las = 1,  
        ylim = c(0, max(freq_table) + 5),  
        names.arg = x_labels) 
```

# Economic Controls

```{r}

#HHInc 

freq_table <- table(data$HHInc)

x_labels <- c("< $20k \n n=708", "$20k-$35k \n n=601", "$35k-$50k \n n=627", "$50k-$75k \n n=835", "$75K+ \n n=2020") 

# Create the barplot
barplot(freq_table, 
        main = "Combined Houshold Income Ranges", 
        xlab = "Ranges", 
        ylab = "Count", 
        col = "lightgreen", 
        border = "white", 
        las = 1,  
        ylim = c(0, max(freq_table) + 5), 
        names.arg = x_labels)  


#Full Time Work
freq_table <- table(data$WorkFullTime)

pie(freq_table, 
    main = "Do you work full time?", 
    col = c("lightblue", "lightgreen"),
    labels = paste(names(freq_table), "\n", freq_table),
    radius = 1, 
    cex = 1.2,  
    clockwise = TRUE,  
    border = "black",  
    init.angle = 90  
)
   
```

## Stratification Assignment
```{r}
#Stratum Classification

freq_table <- table(data$STRATUM)

pie(freq_table, 
    main = "STRATUM ASSIGNMENT", 
    col = c("lightblue", "lightgreen", "lightpink", "lightyellow"),
    labels = paste(names(freq_table), "\n", freq_table),
    radius = 1, 
    cex = 0.75,  
    clockwise = TRUE,  
    border = "black",  
    init.angle = 270
)
```

# More Recoding for Data Analysis
```{r}
#ACCESS TYPE
table(data$InternetAccessType)
data$InternetAccessType_dummy <- ifelse(data$InternetAccessType == 4, 1, 0)
table(data$InternetAccessType_dummy)


# DEVICE
table(data$HAVEDEVICE_CAT)
data$HAVEDEVICE_CAT_recode <- ifelse(data$HAVEDEVICE_CAT == 3, 0,
                                     ifelse(data$HAVEDEVICE_CAT == 4, 2, 1))
table(data$HAVEDEVICE_CAT_recode)

#VISTIED
table(data$SocMed_Visited)
data$SocMed_Visited <- as.numeric(data$SocMed_Visited)

#CONFIDENCE
table(data$ConfidentInternetHealth)
data$ConfidentInternetHealth <- as.numeric(data$ConfidentInternetHealth)

#RACE
table(data$RaceEthn5)
data$RaceEthn5_recoded <- factor(data$RaceEthn5, 
                         levels = c(1, 2, 3, 4, 5),
                         label = c("NHWhite", "NHBlack", "Hispanic", "NHAsian", "NHOther"))

# Check the table after factoring
table(data$RaceEthn5_recoded)

#EDUCATION
table(data$EducA)
data$EducA_recoded <- factor(data$EducA, 
                         levels = c(1, 2, 3, 4),
                         label = c("< High School", "HS Grad", "Some College", "College Grad +"))

# Check the table after factoring
table(data$EducA_recoded)

#CHILDREN
data$ChildrenInHH_recode <- as.numeric(data$ChildrenInHH_recode)
```



# LOGIT REGRESSIONS
```{r}
# Logistic Regression Models

## Model 1: Frequency of internet usage as a predictor
model1 <- glm(Electronic2_HealthInfo ~ SocMed_Visited , family = binomial, data = data)
summary(model1)


## Model 2: Alongside Controls
model2 <- glm(Electronic2_HealthInfo ~ SocMed_Visited +
                InternetAccessType_dummy + HAVEDEVICE_CAT_recode + ConfidentInternetHealth + 
                MisleadingHealthInfo, family = binomial, data = data)
summary(model2)


## Model 3: Adding demographic factors
model3 <- glm(Electronic2_HealthInfo ~ SocMed_Visited +
                InternetAccessType_dummy + HAVEDEVICE_CAT_recode + ConfidentInternetHealth + 
                MisleadingHealthInfo +
                HealthStatus+ Age+ BirthGender+ RaceEthn5_recoded+ EducA_recoded + PR_RUCA_2010 +
                ChildrenInHH_recode, family = binomial, data = data)
summary(model3)

## Model 4: Adding demographic and economic factors
model4 <- glm(Electronic2_HealthInfo ~ SocMed_Visited +
                InternetAccessType_dummy + HAVEDEVICE_CAT_recode + ConfidentInternetHealth + 
                MisleadingHealthInfo +
                HealthStatus+ Age+ BirthGender+ RaceEthn5_recoded+ EducA_recoded + PR_RUCA_2010 +
                ChildrenInHH_recode + HHInc + WorkFullTime, family = binomial, data = data)
summary(model4)
```
# SUMMARY OF MODEL $
```{r}
model_sum <- list("Model 4" = model4)
modelsummary(model_sum, output = "huxtable")
```

# SUMMARY OF ALL MODELS
```{r}
model_list<-list("Baseline" = model1, "Health Related Controls" = model2, 
                 "Add Demographics" = model3,
                 "Add Economics" = model4)
modelsummary(model_list, output = "huxtable")
```
# GLOBAL F TEST

```{r}
anova(model3, model4)
```


# MARGINAL EFFECTS

## AVERAGE PREDICTIONS
```{r}
predicitions <- avg_predictions(model4, variables='SocMed_Visited')|>
  tibble()

predicitions
```

```{r}
#put in presentable table

predictions <- avg_predictions(model4, variables = 'SocMed_Visited') |>
  tibble()

predictions$SocMed_Visited <- c("Never", "Rarely", "Occasionally", "Frequently", "Every Day")

# Create and display the table with custom row names
predictions |>
  gt() |>
  tab_header(
    title = "Average Predicted Probabilities for SocMed_Visited",
    subtitle = "Based on Logistic Regression Model"
  ) |>
  fmt_number(
    columns = everything(),
    decimals = 3
  ) |>
  cols_label(
    SocMed_Visited = "Social Media Usage",
    estimate = "Estimate",
    std.error = "Std. Error",
    statistic = "Statistic",
    p.value = "P-value",
    s.value = "S-value",
    conf.low = "Conf. Low",
    conf.high = "Conf. High"
  )

```

## COUNTERFACTUAL APPROACH

```{r}
mfx <- avg_comparisons(model4) |> 
  tidy() |> 
  mutate(contrast = paste(term, ":", contrast))

mfx_significant <- mfx |> 
  filter(p.value < 0.05)

ggplot(mfx_significant, aes(x = estimate, y = contrast, color= "Model 4",
                xmin = conf.low, 
                xmax = conf.high)) + 
  geom_pointrange(position = position_dodge(width = 0.5)) + 
  theme_bw() + 
  xlim(c(-0.5, 0.5)) + 
  geom_vline(xintercept = 0, lty = 2) + 
  scale_color_brewer(palette = "Dark2") + 
  labs(
    title = "Marginal Effects of Significant Coefficients",
    caption = "Averaged over observed values"
  ) + 
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_text(size = 10)
  )
```


# CHECK THE MARGINAL EFFECTS
```{r}

#HIGH SM USAGE
logit_effect1 <-predict(model4, 
                         newdata=data.frame(
                           SocMed_Visited = 5,
                           InternetAccessType_dummy = 1,
                           HAVEDEVICE_CAT_recode = 2,
                           ConfidentInternetHealth =5,
                           MisleadingHealthInfo = "5",
                           HealthStatus = 1,
                           BirthGender= 0,
                           RaceEthn5_recoded = "NHWhite",
                           EducA_recoded = "College Grad +",
                           PR_RUCA_2010 = 1,
                           HHInc = 5,
                           Age = 56,
                           WorkFullTime= 1,
                           ChildrenInHH_recode = 0),
                           type='response')


logit_effect2 <-predict(model4, 
                         newdata=data.frame(
                           SocMed_Visited = 5,
                           InternetAccessType_dummy = 0,
                           HAVEDEVICE_CAT_recode = 0,
                           ConfidentInternetHealth =1,
                           MisleadingHealthInfo = "1",
                           HealthStatus = 0,
                           BirthGender= 1,
                           RaceEthn5_recoded = "NHBlack",
                           EducA_recoded = "< High School",
                           PR_RUCA_2010 = 0,
                           HHInc = 1,
                           Age = 56,
                           WorkFullTime= 1,
                           ChildrenInHH_recode = 0),
                           type='response')

logit_effect1- logit_effect2 



# LOW SM USAGE
logit_effect3 <-predict(model4, 
                         newdata=data.frame(
                           SocMed_Visited = 1,
                           InternetAccessType_dummy = 1,
                           HAVEDEVICE_CAT_recode = 2,
                           ConfidentInternetHealth =5,
                           MisleadingHealthInfo = "5",
                           HealthStatus = 1,
                           BirthGender= 0,
                           RaceEthn5_recoded = "NHWhite",
                           EducA_recoded = "College Grad +",
                           PR_RUCA_2010 = 1,
                           HHInc = 5,
                           Age = 56,
                           WorkFullTime= 1,
                           ChildrenInHH_recode = 0),
                           type='response')


logit_effect4 <-predict(model4, 
                         newdata=data.frame(
                           SocMed_Visited = 1,
                           InternetAccessType_dummy = 0,
                           HAVEDEVICE_CAT_recode = 0,
                           ConfidentInternetHealth =1,
                           MisleadingHealthInfo = "1",
                           HealthStatus = 0,
                           BirthGender= 1,
                           RaceEthn5_recoded = "NHBlack",
                           EducA_recoded = "< High School",
                           PR_RUCA_2010 = 0,
                           HHInc = 1,
                           Age = 56,
                           WorkFullTime= 1,
                           ChildrenInHH_recode = 0),
                           type='response')

logit_effect3- logit_effect4 
```


# DIAGNOSTICS AND ROBUSTNESS CHECKS

Muliti-colinearity 
```{r}
vif(model4)
```
Autoplot
```{r}
autoplot(model4)
```

Robust Standard Errors
```{r}
robust_se <- sqrt(diag(vcovHC(model4, type = "HC0")))
coefficients <- coef(model4)  # Get model coefficients
z_stats <- coefficients / robust_se
conf_int_low <- coefficients - 1.96 * robust_se
conf_int_high <- coefficients + 1.96 * robust_se

results_table <- data.frame(
  Variable = names(coefficients),
  Coefficient = coefficients,
  Robust_SE = robust_se,
  Z_Statistic = z_stats,
  Conf_Low = conf_int_low,
  Conf_High = conf_int_high
)


# Create the table and format it
results_table %>%
  gt() %>%
  tab_header(
    title = "Robust Standard Errors and Model Statistics"
  ) %>%
  cols_label(
    Variable = "Coefficient",
    Coefficient = "Estimate",
    Robust_SE = "Robust SE",
    Z_Statistic = "Z-Statistic",
    Conf_Low = "95% Conf. Low",
    Conf_High = "95% Conf. High"
  ) %>%
  fmt_number(
    columns = vars(Coefficient, Robust_SE, Z_Statistic, Conf_Low, Conf_High),
    decimals = 3
  )



```





