---
title: "Homework One"
author: "Yael Beshaw"
date: "2025-01-02"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Necessary Packages
```{r}
library(tidyverse)
library(tidycensus)
```

Use the FiveThirtyEight presidential elections data to answer the following questions about the 2020 general election results.
```{r}
url<-"https://raw.githubusercontent.com/fivethirtyeight/election-results/main/election_results_presidential.csv"

presidential_elections<-read_csv(url)
```

Question One: 

Create a data frame with the two party vote share and the winning candidate for 
each state (plus D.C.) in the 2020 presidential election.

```{r}
election_2020 <- presidential_elections|>
  select(cycle, stage, state, candidate_name, votes, winner)|> 
  #select columns of interest
  filter(cycle==2020)|> #2020 
  filter(stage== "general")|> #presidential election
  filter(!is.na(state)) #each state + D.C.
```

```{r}
pres_2020 <- election_2020|>
  select(state, candidate_name, votes)|> #filter the df columns
  group_by(state) |> #organize by state
  filter(candidate_name %in% c("Joe Biden", "Donald Trump"))|> #two party
  filter(str_detect(state, "CD-[0-9]") ==FALSE) #remove CD's for Maine/Nebraska
```

```{r}
#troubleshoot
#issue where "New York" was duplicated, assuming it did not filter out
#state vs city

pres_2020 <- pres_2020|>
  filter(!(state == "New York" & candidate_name == "Joe Biden" & 
             votes == 386010))|>
  filter(!(state == "New York" & candidate_name == "Donald Trump" & 
             votes == 	295657))

#utilize pivot wider to show vote shares between Trump and Biden
pres_wide <- pres_2020|>
  pivot_wider(names_from = candidate_name, 
              values_from = votes)|>
  arrange(state) #alphabetical order

pres_wide
```



Question Two:
Use the data frame you created in the prior step to calculate Biden’s share of 
the two-party vote in each state (i.e. Biden votes / (Biden votes + Trump votes) 
```{r}
new_pres2020 <- pres_wide|>
  mutate(`Biden's Share`= `Joe Biden`/(`Joe Biden` + `Donald Trump`))

new_pres2020
```
Question Three: 

Use the following code to download the ACS estimated median household income for
each state and then use a join to add this column to your data. 
```{r}
median_income <- get_acs(geography = "state", 
                         variables = c(median_income = "B19013_001"), 
                         year = 2020)
```

```{r}
votes_and_median <-new_pres2020|>
  left_join(median_income, by=join_by(state == NAME))|>
  mutate(`Median Household Income`= estimate)|>
  select(state, `Donald Trump`, `Joe Biden`, `Biden's Share`, 
         `Median Household Income`)
```

Question Four:

Run a linear regression to calculate the effect of median income on Biden’s 
statewide two party vote share. Produce a formatted table to display your 
results and briefly discuss your findings.
```{r}
library(flextable)
model<-lm(`Biden's Share` ~ `Median Household Income`  , data= votes_and_median)
summary(model)
```
As seen in the table below, for every one unit increase in the median household
income of a state (including D.C.) in the United States. The expected mean for
Biden's Share of the vote goes up by 7.98e-06 units. This is statistically 
significant as we observe the p-value to less than 0.05 and we therefore reject 
the null hypothesis that there is is no effect of median household income. While
the effect of the median household income seems small, it is rather much larger
when we consider that the unit of measure is in dollars. Thus, a state that has
a median household value around $25,000 greater than another
(i.e., Alabama vs Alaska), we can estimate that Biden's Vote Share increases by
0.1996 or almost 20%.
```{r}
as_flextable(model)
```
