---
title: "GVPT728 HW#4"
author: "Yael Beshaw"
date: "2025-01-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Download Data of Interest
```{r, message=FALSE}
library(tidyverse)
library(modelsummary)
socpoc <- dataverse::get_dataframe_by_name(
  filename = "socpocAPSR.csv",
  .f=read_csv,
  dataset = "10.7910/DVN/CRPAA8&version=1.0", 
  server = "dataverse.harvard.edu")|>
  select(-1)
```

# Question 1

*Estimate the following bivariate model using a linear probability model and a* 
*logit or probit model*

```{r}
lpm <- lm(supply_dummy ~ own , data = socpoc)

logit <- glm(supply_dummy ~ own , data = socpoc, 
             family = binomial)

probit <- glm(supply_dummy ~ own , data = socpoc, 
             family = binomial(link= "probit"))
```

## Comparision of Models
```{r}
compare<-list("Linear Probability" = lpm, "Logit" = logit, "Probit"= probit)
modelsummary(compare, output = "huxtable")
```



# Question 1a

What is the estimated effect of home-ownership on the probability that a 
respondent supports reduced restrictions on building new housing in this model? 
(state your answer in terms of the difference in % probability). Note any* 
differences between your three models.*

## *Linear Probability Model*

The estimated effect of home-ownership on the probability that a 
respondent supports reduced restrictions on building new housing in the
Linear Probability Model is 31.2% lower than that of non-homeownership.

## *Logit Model*

The estimated effect of home-ownership that a respondent supports reduced 
restrictions on building new housing in the Logit Model 31.2% less compared to 
non-homeownership.

```{r}
coefs<-coef(logit)
logit_pred0 <- coefs["(Intercept)"]
logit_pred1 <- coefs["(Intercept)"] + coefs['own'] * 1 

pred_prob0 <- 1/(1+exp(-logit_pred0))
pred_prob1 <-1/(1+exp(-logit_pred1))

pred_prob0-pred_prob1
```

## *Probit Model*

Similar to the other two models, the estimated effect of home-ownership that a
respondent supports reduced restrictions on building new housing in the Probit 
Model 31.2% less compared to non-homeownership.
```{r}
coefs<-coef(probit)

probit_pred0 <- coefs["(Intercept)"]
probit_pred1 <- coefs["(Intercept)"] + coefs['own'] * 1 

probit_prob0 <- probit$family$linkinv(probit_pred0) 
probit_prob1 <- probit$family$linkinv(probit_pred1)

probit_prob0 - probit_prob1
```

## *Differences in the Models*

The main differences in the models is that in our huxtable we see that that the
linear probability model is the only one where the information for the intercept
and the coefficents is directly interpretable. However, conducting predicited
probabilities for both the logit and probit model, we see that we observe the
same effect of predicted probability for a homeowner supporting reduced 
restrictions on building new housing. The logit and probit models both have the
same BIC and AIC which is lower than that of the linear probabilities model.
This indicates that the logit/probit may be a better model, however, the F
statisitc for the probit is slightly higher than that of the logit, indicating
that it may be the better fit overall.



# Question 2

*Estimate a linear probability and logit/probit model with the same dependent* 
*variable, but include additional controls for ideology, white (non-hispanic)* 
*and income:*

```{r}
lpm_new <- lm(supply_dummy ~ own + ideology + whitenh + income , data = socpoc)

logit_new <- glm(supply_dummy ~ own + ideology + whitenh + income , 
                 data = socpoc,
                 family= binomial)

probit_new <- glm(supply_dummy ~ own + ideology + whitenh + income , 
                 data = socpoc,
                 family= binomial(link="probit"))
```

## Comparision of Models
```{r}
compare<-list("Linear Probability" = lpm_new, "Logit" = logit_new, 
              "Probit"= probit_new)

modelsummary(compare, output = "huxtable")
```




# Question 2a

What is the marginal effect of homeownership for a non-white “Extremely
Conservative” respondent whose household income is less than $5,000 per year? 
Compare and contrast the estimates from the linear probability model and the
logit/probit model.*

## *Linear Probability Model*

The marginal effect of homeownership for a non-white “Extremely 
Conservative” respondent whose household income is less than $5,000 per year on
on the probability that the respondent supports reduced restrictions on building
new housing in the Linear Probability Model is 27.4% lower than that if they 
were a non-homeowner.

```{r}
#marginal effect of linear probability model: -0.274
coef(lpm_new)["own"] 
```

## *Logit*

The marginal effect of homeownership for a non-white “Extremely 
Conservative” respondent whose household income is less than $5,000 per year on
on the probability that the respondent supports reduced restrictions on building
new housing in the Logit Model is 27.2% lower than that if they were
a non-homeowner.

```{r}
#marginal effect of logit model: -0.272
logit_effect_owner <-predict(logit_new, 
                         newdata=data.frame(
                           own = 1,
                           income = 1,
                           whitenh = 0,
                           ideology = 1), type='response')

logit_effect_nonowner <-predict(logit_new, 
                         newdata=data.frame(
                           own = 0,
                           income = 1,
                           whitenh = 0,
                           ideology = 1), type='response')

logit_effect_owner- logit_effect_nonowner  
```


## *Probit*

The marginal effect of homeownership for a non-white “Extremely 
Conservative” respondent whose household income is less than $5,000 per year on
on the probability that the respondent supports reduced restrictions on building
new housing in the Probit Model is 27.3% lower than that if they were
a non-homeowner.

```{r}
#marginal effect of probit model: -0.273
probit_effect_owner <-predict(probit_new, 
                         newdata=data.frame(
                           own = 1,
                           income = 1,
                           whitenh = 0,
                           ideology = 1), type='response')

probit_effect_nonowner <-predict(probit_new, 
                         newdata=data.frame(
                           own = 0,
                           income = 1,
                           whitenh = 0,
                           ideology = 1), type='response')

probit_effect_owner- probit_effect_nonowner  
```

## *Differences in the Models*
The estimates are all around -27% across the three models. All three models
show the same positive vs negative effect of each predictor. However, as
seen in Question #1, the Probit model still has the lowest AIC and BIC out
of the three with the highest logged likelihood, indicating that it is the
model with the best fit.


# Question 2b

Finally, estimate the average effect of homeownership across all observations 
using the observed values/counterfactual approach. Note any differences in your 
results.

## *Linear Probability Model*

The average effect of homeownership is a is a 27.4% decrease in the 
probability of support of reduced restrictions on building new housing.

```{r}
homeownership <- replace(lpm_new$model, "own", values=1)
non_homeownership <- replace(lpm_new$model, "own", values=0)

diffs<-predict(lpm_new, newdata=non_homeownership, type='response') - 
  predict(lpm_new, newdata=homeownership, type='response')

mean(diffs)
```


## *Logit*

The average effect of homeownership is a is a 27.1% decrease in the 
probability of support of reduced restrictions on building new housing.
This is slightly lower than the marginal effect of 27.2%
```{r}
homeownership <- replace(logit_new$model, "own", values=1)
non_homeownership <- replace(logit_new$model, "own", values=0)

diffs<-predict(logit_new, newdata=non_homeownership, type='response') - 
  predict(logit_new, newdata=homeownership, type='response')

mean(diffs)
```

## *Probit*

The average effect of homeownership is a is a 27.2% decrease in the 
probability of support of reduced restrictions on building new housing. This
is slightly lower than the marginal effect of 27.3%

```{r}
homeownership <- replace(probit_new$model, "own", values=1)
non_homeownership <- replace(probit_new$model, "own", values=0)

diffs<-predict(probit_new, newdata=non_homeownership, type='response') - 
  predict(probit_new, newdata=homeownership, type='response')

mean(diffs)
```




