---
title: "GVPT728 HW#4"
author: "Yael Beshaw"
date: "2025-01-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Download Data of Interest
```{r}
library(tidyverse)
socpoc <- dataverse::get_dataframe_by_name(
  filename = "socpocAPSR.csv",
  .f=read_csv,
  dataset = "10.7910/DVN/CRPAA8&version=1.0", 
  server = "dataverse.harvard.edu")|>
  select(-1)
```

# Question 1
Estimate the following bivariate model using a linear probability model and a logit or probit model.
```{r}

```
What is the estimated effect of home-ownership on the probability that a respondent supports reduced restrictions on building new housing in this model? (state your answer in terms of the difference in % probability). Note any differences between your three models.

# Question 2
Estimate a linear probability and logit/probit model with the same dependent variable, but include additional controls for ideology, white (non-hispanic) and income:
```{r}

```

## Question 2a
What is the marginal effect of homeownership for a non-white “Extremely Conservative” respondent whose household income is less than $5,000 per year? Compare and contrast the estimates from the linear probability model and the logit/probit model.

## Question 2b
Finally, estimate the average effect of homeownership across all observations using the observed values/counterfactual approach. Note any differences in your results.

